Theoretical evaluation of the potential advantages of cloud IDEs for research and didactics

### 2019-06-21 che.tex
minor fixes, printable version

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into projects, which solve some of the very specialized tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyze problems.
With their changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of down-scaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspace could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid usually on both workload and storage. 
\subsection{Knowledge Required}
The primary problem with Che is the requirement for an already dense knowledge of cloud related technology.
Setting up the Workspace, docker-images, build and CI scripts is a complex topic and can not be done by someone getting started. 
This requirement extends when working with a multi-pod-environment. 
While most of the tasks are by themselves rather simple, the bare amount of such tasks (especially when migrating an existing project to Che) requires a broad knowledge.
This can be done by a single expert user, enabling the other developers  to  use  the  build-routines and  environments provided. 
However, many problems which arise are related to the cloud-environment and will be hard to solve by a novice user, making him dependent on the expert. 
It's therefore necessary to get everyone on a certain base-level to solve their own problems, otherwise the expert will be overloaded and the project stuck.

>>>>

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into projects, which solve some of the very specialized tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyze problems.
With their changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of down-scaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspace could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid usually on both workload and storage. 
\subsection{Knowledge Required}
The primary problem with Che is the requirement for an already dense knowledge of cloud related technology.
Setting up the Workspace, docker-images, build and CI scripts is a complex topic and can not be done by someone getting started. 
This requirement extends when working with a multi-pod-environment. 
While most of the tasks are by themselves rather simple, the bare amount of such tasks (especially when migrating an existing project to Che) requires a broad knowledge.
This can be done by a single expert user, enabling the other developers  to  use  the  build-routines and  environments provided.
